\myshort{} to Enable Systematic Evaluation of Testing Techniques

### 2025-03-21 paper/main.tex
Added total column

\begin{table}
  \centering
  \caption{\label{table:bug-stats}Different bug manifestation types
    from \tname.\Fix{If time allows, add a total column and sort rows
      according to it (except incorrect output)}}
  \begin{tabular}{lrrrr}\toprule
    Bug manifestation type &Jax &Pytorch &Tensorflow \\\midrule
    Incorrect Output &14 &11 &5 \\
    Internal Exception &11 &9 &4 \\
    Value Error &7 &0 &4 \\
    Type Error &3 &2 &3 \\
    Attribute Error &2 &0 &2 \\
    Index Error &2 &1 &0 \\
    Floating Point Error &1 &0 &0 \\
    Error Not Raised &1 &0 &0 \\
    Parse Error &1 &0 &0 \\
    Runtime Warning &1 &0 &0 \\
    Not Implemented Error &1 &0 &0 \\
    Memory Error &1 &1 &0 \\
    Invalid Argument Error &1 &0 &1 \\
    Runtime Error &0 &7 &1 \\
    Assertion Error &0 &2 &0 \\
    Segmentation Fault &0 &2 &1 \\
    Floating Point Exception &0 &1 &0 \\
    Aborted &0 &1 &8 \\
    \midrule
    $\Sigma$ &\numjaxbugs{} &\numtorchbugs{} &\numtfbugs{} \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}
  \centering
  \caption{\label{table:bug-stats}Different bug manifestation types
    from \tname.}
  \begin{tabular}{lrrrrr}\toprule
    Bug manifestation type &Jax &Pytorch &Tensorflow &Total \\\midrule
    Incorrect Output &14 &11 &5 &30 \\
    Internal Exception &11 &9 &4 &24 \\
    Value Error &7 &0 &4 &11 \\
    Type Error &0 &1 &8 &9 \\
    Attribute Error &3 &2 &3 &8 \\
    Index Error &0 &7 &1 &8 \\
    Runtime Error &2 &0 &2 &4 \\
    Memory Error &2 &1 &0 &3 \\
    Invalid Argument Error &0 &2 &1 &3 \\
    Floating Point Error &1 &1 &0 &2 \\
    Error Not Raised &1 &0 &1 &2 \\
    Parse Error &0 &2 &0 &2 \\
    Runtime Warning &1 &0 &0 &1 \\
    Not Implemented Error &1 &0 &0 &1 \\
    Assertion Error &1 &0 &0 &1 \\
    Segmentation Fault &1 &0 &0 &1 \\
    Floating Point Exception &1 &0 &0 &1 \\
    Aborted &0 &1 &0 &1 \\
    \midrule
    $\Sigma$ &\numjaxbugs{} &\numtorchbugs{} &\numtfbugs{} &\numbugs{} \\
    \bottomrule
  \end{tabular}
\end{table}
